---
title: "BirthBias"
output: html_notebook
---

The birth data is only for babies, no mothers, so there is no age difference.

## 1. Load data
```{r}
library(bigmemory)
data<-read.delim("~/Desktop/BigData_ProjectData/SPARCS-2017-birth-Bias.csv")
data<-na.omit(data)
```

## 2. Process factor data
Including:
county,gender,race,ethnity,admission,disposition,severity,mortality,emergency
```{r}
y<-data$Average.Charges
# area<-as.factor(data$Hospital.Service.Area)
county<-as.factor(data$Hospital.County)
# facility<-as.factor(data$Facility.Name)
gender<-as.factor(data$Gender)
race<-as.factor(data$Race)
ethnity<-as.factor(data$Ethnicity)
admission<-as.factor(data$Type.of.Admission)
disposition<-as.factor(data$Patient.Disposition)
severity<-factor(data$APR.Severity.of.Illness.Description,order=TRUE,level=c("Minor", "Moderate", "Major", "Extreme"))
mortality<-factor(data$APR.Risk.of.Mortality,order=TRUE,level=c("Minor", "Moderate", "Major", "Extreme"))
emergency<-as.factor(data$Emergency.Department.Indicator)
birthweight<-data$Birth.Weight
```

```{r}
interaction.plot(ethnity,race,y)
interaction.plot(severity,mortality,y)
```


## anova on race
```{r}
fit1<-lm(y~race+county+gender+ethnity+admission+disposition+severity+mortality+emergency+birthweight)
```

```{r}
summary(fit1)
```
```{r}
anova(fit1)
```
race+county+gender+ethnity+admission+disposition+severity+mortality+emergency+birthweight

relatively speaking (also from distribution), admission & emergency disposition+severity+mortality all could ignore.

## Multi-level comparison
```{r}
fit<-aov(y~race+county+gender+ethnity+disposition+severity+mortality+emergency)
summary(fit)
```
```{r}
TukeyHSD(fit)
```

```{r}
```


```{r}
fit3<-lm(y~race*county)
```

```{r}
aov_fit3<-aov(fit3)
summary(aov_fit3)
```


```{r}
TukeyHSD(aov_fit3)
```

